

%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Van Cleef \& Arpels, Inc.}{USA - New York\\
\vspace{4mm}
Coordinator, High Jewelry\\Reference code USVCA - 00029613}
\date{June 28, 2014}
\opening{Dear Sir or Madam,}
\closing{Yours sincerely,}
% use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle


I would like to express my interest in the High Jewelry Coordinator position.  As the current Head of Catalogue Production/Cataloguer for Sotheby’s Jewelry Department, in Geneva, Switzerland, I believe I would bring valuable professional experience and skills to the position.


I have chosen to leave Switzerland and return to the United States in order to be closer to family, and this transition gives me the opportunity to explore new areas within the High Jewelry profession. Over the three and a half years I have been with Sotheby’s, I have worked with some of the world's most important jewels, many of them by Van Cleef \& Arpels. I am applying for this position due to the respect and admiration I have for your company's creations.


The skills I have gained in my current position would help me to excel in the role of Coordinator.  At present, I am responsible for organizing pre-sale public exhibitions. This demanding undertaking requires an array of skills include training and managing more than thirty temporary employees, deciding on the ‘mis-en-sc\`{e}ne’ of jewels within their showcases, selecting visuals, and managing client services including VIPs. Such experiences would prove valuable in my Coordinator work, especially in regard to the implementation of High Jewelry action plans, sales training, client treatment, and supporting the boutique network.


My daily tasks as Head Cataloguer have also helped me to refined strong communication skills, something I find essential to all work. I  work closely with the Press and Marketing departments, assisting in the creation, proofing and approval of outgoing materials. This work is done in French, English, and occasionally Italian. Together with the production of our bi-annual catalogues, which require long hours and meticulous attention to detail, I believe my experiences and skills make me a strong candidate for the Coordinator position.


My r\'{e}sum\'{e} further details my relevant qualifications. I welcome the opportunity to discuss the position further with you, and I can be reached by email or phone at your convenience. Thank you for your time and consideration.


\makeletterclosing

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}
